\documentclass{tccv}
\usepackage[english]{babel}

\title{Aaron de Windt Resume}
\begin{document}

\part{Aaron Miguel de Windt}

\section{Experience}

\begin{eventlist}


\event{September 2019 -- Present}
    {Dawn Aerospace, Delft}
    {Control and software engineer}
\begin{itemize}
   \item{Responsible for the development of aircaft system \linebreak identification tools in Python.}
   \item{Developed internal enineering management web applications using Flask.}
   \item{Responsible for the development of the thrust vector control algorithms and software for a small satellite propulsion system. Moslty embedded programming in C/C++ with simulations in Python.}
\end{itemize}

\event{August 2019 -- December 2019}
     {Delft Aerospace Rocket Engineering, Delft}
     {SPEAR Software engineer}
\begin{itemize}
    \item{Supersonic Parachute Experiment Aboard REXUS, the goal is to flight test the Stratos III/IV Hemisflo drogue parachute at supersonic conditions as part of the REXUS/BEXUS program.}
    \item{Developed the ground station software using Python and QT.}
\end{itemize}

\event{August 2018 -- August 2019}
     {Airborne Composite Automation, The Hague}
     {Software engineer}
\begin{itemize}
    \item{Responsible for the development of control software for machines used to automate the production of composite parts, primirally in written Python.}
\end{itemize}

\event{September 2016 -- August 2018}
     {Delft Aerospace Rocket Engineering, Delft}
     {Chief Simulations Stratos III}
\begin{itemize}
    \item{At the time the largest student rocket ever built with the goal of breaking the European altitude record.}
    \item{Responsible for the development, operation and maintanance of a set of simulation tools primirally written in Python with C++ extensions.}
    \item{In charge of over eight part-time engineers.}
    \item{Worked on the preliminary and detailed design of \linebreak Stratos~III.}
    \item{Responsible of a state estimation and sensor fusion experiment using Kalman filters written in C++.}
    \item{Responsible for the range safety analysis of Stratos~III.}
    \item{Produced miscellaneous hardware parts, primirally \linebreak composite parts, metal machining and assembly of the hybrid rocket engine.}
\end{itemize}

\end{eventlist}

% \personal
%     % [costahuang.me]
%     {Korvezeestraat 224, 2628DK, Delft \newline Netherlands }
%     {+31 6 47 630 507}
%     {aaron.dewindt@gmail.com}
%     {www.linkedin.com/in/aaron-de-windt}
%     {https://github.com/aarondewindt}

\section{Personal}
\begin{factlist}
    \item{Date of Birth}
         {March 31st 1992}
    \item{Nationality}
         {Dutch}
\end{factlist}

\section{Education}

\begin{yearlist}

\item[Expected 2021 \hspace*{\fill} \linebreak Thesis: Orbital ascent trajectory optimization using reinforcement learning]
    {2015 -- Present}
    {MSc Aerospace Control and Simulations}
    {Delft University of Technology}

\item{2011 -- 2015}
    {BSc Aerospace Engineering}
    {Delft University of Technology}

\end{yearlist}

% \section{Public projects}

% \begin{yearlist}

% \item{2018}
%      {\href{https://github.com/vwxyzjn/jupyter_disqus}{Jupyter\_disqus}}
%      {Add Disqus to Jupyter Notebook}

% \item{2017}
%      {\href{https://costahuang.me/SC2AI/}{SC2AI}}
%      {Machine learning for StarCraft II AI}

% \item{2017}
%      {\href{https://costahuang.me/LP_optimization_python/}{LP\_optimization\_python}}
%      {Linear programming for scheduling}

% \item{2017}
%      {\href{https://vuetifyjs.com/themes/parallax-starter/}{Parallax Template}}
%      {Web design template}

% \item{2017}
%      {\href{https://streettraffic.org/}{StreetTraffic}}
%      {Python library that crawls traffic data}

% \item{2016}
%      {\href{https://costahuang.me/Sentiment-Analysis-LSTM/}{Sentiment-Analysis-LSTM}}
%      {Movie reviews classification}

% \item{2016}
%      {\href{https://github.com/vwxyzjn/penspider}{Penspider}}
%      {Web crawler that collects listings of pens }

% \end{yearlist}

% \section{Repositories Contributed}

% \begin{factlist}
% \item{Reinforceio/tensorforce}{\href{https://github.com/reinforceio/tensorforce/pull/242}{\#242}, \href{https://github.com/reinforceio/tensorforce/pull/244}{\#242}}
% \item{Microsoft/vscode-python}{\href{https://github.com/DonJayamanne/pythonVSCode/issues/1101}{\#1101}}
% \item{Vuetifyjs/docs}{\href{https://github.com/vuetifyjs/docs/pull/181}{\#181}}
% \end{factlist}

\section{Languages}

\begin{factlist}
    \item{Papiamentu}{Native speaker}
    \item{English}{Fluent}
    \item{Dutch}{Good}
    \item{Spanish}{Good}
\end{factlist}


\section{Technical skills}
% \begin{itemize}
%     \item{Programming}
%     \item{Control theory}
%     \item{Machine learning}
%     \item{Systems Engineering}
%     \item{Metal working (Sheet metal and turning)}
%     \item{Carbon/glass fiber composite materials production}
%     \item{Bench-work}
% \end{itemize}

Programming, Control theory, Machine learning, Systems Engineering, Metal working, Carbon/glass fiber composite materials production, Bench-work


\section{Software skills}

\begin{factlist}

\item{Proficient}
     {Python, C/C++, Matlab, Git, \LaTeX, Simulink, Linux, Windows, Numpy, Pandas, XArray, Scipy, Jupyter}

\item{Working Knowledge}
     {Tensorflow, RLlib, JSBSim, FreeRTOS, HTML, Javascript, CSS, SQL, Microsoft/Libre office, Flask, Qt, CATIA}

\item{Familiar}
     {Rust, OpenCV, PHP, Siemens PLC Programming}

\end{factlist}

% \section{References}
% Filipe Barreiro\\
% Development Engineer\\
% filipe.barreiro@rocketfactory-augsburg.com\\
% +49 821 999 576 19


\newpage
\onecolumn
\section{Experience (Continued)}
\begin{eventlist}

\event{Febuary 2018 -- June 2018}
    {DAWN Aerospace, Delft}
    {Control and Simulation intern}
\begin{itemize}
   \item{Researched into the development of aircaft system identification tools and developed tools demonstrating the methods found.}
\end{itemize}

\event{September 2017 -- January 2018}
    {Delft Aerospace Rocket Engineering, Delft}
    {DARE Minor Supervisor}
\begin{itemize}
   \item Minor program organized by DARE with the goal to design, produce and test a rocket engine trust vectoring system.
   \item Supervised and provided technical guidance to the DARE Minor 2017/2018 team.
\end{itemize}

\event{September 2017 -- September 2018}
     {Delft Aerospace Rocket Engineering, Delft}
     {Secretary Executive Safety Board}
\begin{itemize}
    \item Responsible for taking minutes and general organization of the DARE safety board.
\end{itemize}

\event{May 2013 -- June 2016}
     {Delft Aerospace Rocket Engineering, Delft}
     {Advanced Control Team Engineer and Co-Founder}
\begin{itemize}
    \item {Co-Founder of the Advanced Control Team (ACT) with the goal to develop a working active stabilization and guidance system for a rocket.}
    \item {In charge of the ACT Control, Software and Electronics department.}
    \item {In charge of over four part-time engineers.}
    \item {Responsible for the development of the flight computer firmware written in C/C++ running on FreeRTOS.}
    \item {Responsible for the development of the ground station software written in C/C++ and Python.}
    \item {Responsible for the development of the trajectory simulation software, primarily written in Python with C++ extensions.}
    \item {Sole developer of the software and hardware in the loop test toolkit. Custom Windows and Linux simulations with RS232 and TCP/IP for communication between the simulation and flight computer/software.}
\end{itemize}



\event{January 2014 -- November 2015}
     {Delft Aerospace Rocket Engineering, Delft}
     {Stratos II and Stratos II+ Simulations teamleader}
\begin{itemize}
    \item {The Stratos II+ Rocket launched in 2015 and successfully broke the European Student Altitude Record.}
    \item {At the time this was the largest student rocket built in Europe.}
    \item {Responsible for the development, operation and maintenance of a set of simulation tools primarily written in Python with C++ extensions.}
    \item{In charge of two part-time engineers.}
    \item{Responsible for the range safety analysis of Stratos II and II+.}
\end{itemize}


\end{eventlist}




\end{document}
